Alone Together: Compositional Reasoning and Inference for Weak Isolation

### 2017-10-26 inference.tex
Edits.

>>>>

A useful instantiation of $\SL$ is $\SL[{\sf BV},{\sf GKS}+{\sf BV}]$,
where ${\sf BV}$ is the theory of bit-vector arithmetic, which is
generally used to encode the finite-bit arithmetic of real programs.
Bit-vector arithmetic has a finite quantifier-free
axiomatization, 
Since {\sf EPR}+{\sf SLA} is known to be decidable~\cite{eprsla}:
\begin{theorem}
  $\SL[{\sf SLA},{\sf EPR}+{\sf SLA}]$ is decidable.
\end{theorem}
The $\SL[{\sf SLA},{\sf EPR}+{\sf SLA}]$ instantiation requires $I$ to
be drawn from {\sf EPR}+{\sf SLA}, which is expressive enough to
describe common database integrity constraints, such as referential
integrity, non-negativeness of all integer values in a column etc.
The isolation specifications presented in \S\ref{sec:isolation} are
already simple first-order formulas that can be encoded in {\sf EPR}.
Furthermore, it is also reasonable to expect the guarantee ($G$) of a
transaction to be expressible in the same logic as its inferred $\F$,
since $\F$ (without the stability check) is essentially a complete
characterization of the transaction, while $G$ is only an abstraction.
Thus, with $\SL[{\sf SLA},{\sf EPR}+{\sf SLA}]$ as the language of
inference, the verification problem for weakly isolated transactions
is decidable. Moreover, off-the-shelf SMT solvers (e.g., Z3) are
equipped with efficient decision procedures for ${\sf EPR}+{\sf SLA}$,
making automated verification a practical exercise.
